### 2014-04-15 paper/exampleobjects.tex

>>>>

\subsection{Speculative Objects and Explorations}

\begin{figure}
\centering
    \includegraphics[width=3.4in]{figures/speculative.png}
\caption{Some possible pipe uses.  The printed whistle in (a) is a Helmholz resonator: it creates a sound when air is blown through the pipe at the front, because air compresses at the small neck joint between the internal chamber and the pipe.  In (b), a capacitor manufactured on a 3D printer coated post-print with copper paint.  This particular one holds an impractically large charge of $>1F$.  (c) gives a comparison of pipe-based resistors, also filled with copper paint.  For a cylindrical wire, resistance is based on its length and cross-sectional area.}
\label{fig:speculative}
\end{figure}

\begin{figure}
\centering
    \includegraphics[width=3.4in]{figures/gates.png}
\caption{By attaching a servo to a gate structure, it is possible to direct fluid through that pipe.  The gate not only has binary positions (a) and (b), but can direct fractional flow, as well (c).}
\label{fig:direct}
\end{figure}

In addition to our six complete examples, we also created some smaller explorations of techniques and possibilities using pipes.

Creating aural outputs using the printed pipes directly is one such possibility: the whistle in Figure \ref{fig:speculative}a is a fully printable audio output which is based on a Helmholz resonator, and which can be activated with air pressure.

Some passive components required in the design of the above circuitry could in the future be created using pipes and printed or injected conductive material.  For example, we printed a proof-of-concept  capacitor which features a thin printed plate with hollow cones on either side (see Figure \ref{fig:speculative}b).  After printing, we coated the inner surfaces of capacitor with copper paint.  It now holds an impractically large charge of $>1F$, but miniturization is possible.  Similarly, tubes can be used to create \emph{resistors} in ``printed'' circuitry: a longer or thinner tube has a greater resistance than a shorter or wider one (see Figure \ref{fig:speculative}c).

Liquids can be mixed in specific concentrations (e.g., for color output) using mixing or splitting topologies along with a servo-controlled gate structure as in Figure \ref{fig:direct}.

Identification of objects is possible using active acoustic sensing \cite{Ono-touchandactivate}: the internal pipes, although not externally visually distinctive, affect the acoustic signature of the object.  While this is an opportunity for record and recall identification, intentional identity encoding using pipes could also be accomplished, through print weight modification using fully enclosed pipes.
